---
title: "HW 2 - Noori Selina"
output:
  pdf_document: default
  html_document: default
date: "2023-09-03"
---

```{r}
options(repos = c(CRAN = "https://cran.r-project.org"))
```


A data table has been created using SQL of popular movies, and ratings collected. The data table was saved as csv, and imported into R using the dplyr package. 
```{r}
# Install and load the "dplyr" package
install.packages("dplyr")
library(dplyr)

# Load the CSV file into an R dataframe
data <- read.csv("/Users/selina/Downloads/movie_ratings.csv")

# Check the loaded data by displaying the table
head(data)  

```
To handle missing data which was initially written as "null" as imported from SQL, "null" has been changed to "NA" which is a better replacement when conducting analysis using R. This way, the code will be able to recognize NA as missing values, and also be able to use in built in functions in further analysis. 

```{r}
# Replace "null" with NA
data[data == "null"] <- NA

# Check the updated dataframe
head(data)
```





