---
title: "Noori Selina Data 607 Assignment 3"
output: html_document
date: "2023-09-13"
---
1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
# Load the College Majors dataset from GitHub
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
college_majors <- read.csv(url)

# Filter for majors containing "DATA" or "STATISTICS"
data_stats_majors <- subset(college_majors, grepl("DATA|STATISTICS", Major))

# Display the majors containing "DATA" or "STATISTICS"
data_stats_majors
```
2. Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
fruits <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

changed <- fruits

# Print the contents of the 'changed' vector
print(changed)
```

3. Describe, in words, what these expressions will match:
(.)\1\1 - This expression will match a string that consists of three consecutive characters. Examples include "AAA" "BBB" 

"(.)(.)\\2\\1" - This expression will match a string of four characters, where the first and the fourth characters are the same, and the second and third characters are the same. An example is "ABBA"

(..)\1 - This expression matches a string with at least four characters where the first two characters repeat at the end, like "ABAB" or "1212."

"(.).\\1.\\1" - This expression matches a string with at least five characters where the first character repeats at both ends, and the middle character is different, like "AXA" or "121."

"(.)(.)(.).*\\3\\2\\1" - This expression matches a string that starts with three characters, followed by any characters, and then repeats the last three characters in reverse order, like "ABCABCBA" or "12344321."


4. Construct regular expressions to match words that:
a. Start and end with the same character.
b. Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
c. Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
library(tidyr)
test_words = list("refer", "pop", "noon", "church", "assessment", "occurrence") 


#Start and end with the same character.
Regex1 = "^(.).+\\1$"
Filter(function(x) any(grepl(Regex1, x)), test_words)
```
```{r}

#Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Regex2 = '\\b\\w*(\\w{2})\\w*\\1'
Filter(function(x) any(grepl(Regex2, x)), test_words)
```
```{r}
#Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
Regex3 = "^[a-z]*([a-z])\\1[a-z]*$"
Filter(function(x) any(grepl(Regex3, x)), test_words)
```

