---
title: "Noori Selina Hw 1"
output:
  pdf_document: default
  html_document: default
date: "2023-09-03"
---
Introduction 

The generic_ballot_averages.csv dataset provides a comprehensive collection of generic ballot polling averages. This dataset offers insights into the preferences of voters in hypothetical elections, without specifying individual candidates, making it a valuable resource for analyzing and understanding voter sentiments towards different political parties in various election cycles or time periods

Article information: https://projects.fivethirtyeight.com/polls/generic-ballot/

```{r}
# Loading the  necessary libraries
library(dplyr)

# Import data through URL
data_url <- "https://projects.fivethirtyeight.com/polls/data/generic_ballot_averages.csv"

# Load the dataset from the URL
df <- read.csv(data_url)

# Display the first few rows of the dataset to get an overview
head(df)

```

Creating Transformations

In this section, we clean and reshape the dataset. We select relevant columns, rename them for clarity, and replace non-intuitive abbreviations. Finally, we showcase the initial rows of the transformed dataset
```{r}
# Load necessary libraries
library(dplyr)

# Load the dataset from the provided URL
data_url <- "https://projects.fivethirtyeight.com/polls/data/generic_ballot_averages.csv"
df <- read.csv(data_url)

# Create a subset of the columns
df_subset <- df %>%
  select(
    candidate,
    pct_estimate,
    lo,
    hi,
    date,
    election,
    cycle
  )

# Rename columns 
df_subset <- df_subset %>%
  rename(
    candidate_name = candidate,
    percentage_estimate = pct_estimate,
    lower_bound = lo,
    upper_bound = hi,
    polling_date = date,
    election_type = election,
    election_cycle = cycle
  )

# Replace any non-intuitive abbreviations if necessary
# For example, if "D" represents Democrats and "R" represents Republicans:
df_subset$candidate_name <- ifelse(df_subset$candidate_name == "D", "Democrats", 
                                    ifelse(df_subset$candidate_name == "R", "Republicans", df_subset$candidate_name))

# Display the first few rows of the transformed dataset
head(df_subset)

```

Conclusion:

Analyzing the dataset of generic ballot polling averages during the 2018 election cycle reveals intriguing insights into voter preferences. On average, the Democrats held a slight lead with an estimated percentage of approximately 43.9%, while the Republicans obtained around 39.5% support. To gain a deeper understanding of the dynamics at play, it is recommended to further investigate the factors influencing shifts in voter sentiment over time. 

